SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2019-02-11 frontrunning/Latex/sections/paper.tex
Updates, ENS still needs more work!

The second category of DApp in Table~\ref{tab:top25DApps} is crypto-collectables. Consider Cryptokitties~\cite{cryptokitties}, the most active DApp in this category and third most active overall. Each kitty (see Appendix~\ref{app:cryptokitty}) is a cartoon kitten with a set of unique features to distinguish it from other cryptokitties, some features are rarer and harder to obtain. They can be bought, sold, or bred with other cryptokitties. At the Ethereum level, the kitty is a token implemented with \textit{ERC-721: Non-Fungible Token Standard}~\cite{erc721}.

%Shayan -> Jeremy: does this make sense? there are more details in the references that due to space limitations cannot be discussed here.
Specific to Cryptokitties protocol, they can breed and give birth. When cryptokitties breed, a variable is set on the pregnant cat to indicate what block the pregnancy will be complete. Anyone calling \texttt{giveBirth()} quickly after the expected birthing time, will receive the birthing reward\footnote{As there are no automated function calls in Ethereum, this incentive model --known as \textit{Action Callback}~\cite{klerosGeneralizedFrontrunner2019}-- is used to encourage users to call these functions.}. Even though front-running these calls would not affect the protocol workflow, but it could result in financial profit for front-runners~\cite{zhou2018erays,cryptoMidwivesBot2018}.

ERC-721 are similar enough to ERC-20 tokens that they can be listed on exchanges that are ERC-20 compatible. To buy a kitty from their main website, the user sends the following bid transaction: \texttt{bid(uint256 \_tokenId)}. This is similar to open auctions and markets on section~\ref{sec:frontrunningExchanges}, bid value and the object (tokenId) bidding on is visible to the network and any user could easily front-run using insertion or displacement attack. The front-runner can see there is an interest in a specific kitty and insert a pair of transactions to buy it and re-auctioning it at a higher price, keeping any profit. %we call this auction-frontrunning.
% https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40

@@

\textsf{Fomo3D} is an example of a game style (known as \textsf{Exit Scam}\footnote{\url{https://exitscam.me/play}}) not based on random outcomes, and it is the most active game on Ethereum in our sample. The aim of this game is to be the last person to have purchased a ticket when a timer goes to zero in a scenario where anyone can buy a ticket and each purchase increases the timer by 30 seconds. Many speculated such a game would never end but on August 22, 2018, the first round of the game ended with the winner collecting 10,469 Ether\footnote{The first winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}} equivalent to \$2.1M USD at the time.
Blockchain forensics indicate a sophisticated winning strategy to displace any new ticket purchases~\cite{fomo3dhacker,fomo3dmedium} that would reset the counter. The winner appears to have started by deploying many high gas consumption DApps unrelated to the game. When the timer of the game reached about 3 minutes, the winner bought 1 ticket and then sent multiple high gasPrice transactions to her own DApps. These transactions congested the network and bribed miners~\cite{mccorry2018smart,bonneau2016buy} to prioritize them ahead of any new ticket purchases in \textsf{Fomo3D} .

@@

The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at disintermediating central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS). For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and front-runners can displace other users attempting to register domains. This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}. \textsf{Ethereum Name Service (ENS)}~\cite{ensEIP} is the most active naming service on Ethereum. Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in the bids, but not the bid amounts. Most implementations use the more user friendly but less confidential method for starting and bidding on a domain name, \texttt{startAuctionsAndBid()}. This method leaks the hash of the domain and the initial bid amount in the auction. Users are allowed to bid for 48 hours before the 48-hour reveal phase begins, in which bidders must send a transaction to reveal their bids for a specific domain. A front-runner using the leaked information can bid with the same amount and reveal prior to the original bidder to win the auction~\cite{ENSHandlingFrontRunningDiscussion}. The auction model is similar to crypto-collectibles auctions in \ref{sec:cryptogames}.

@@

\subsection{Data Collection and Analysis}
According to the analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started. When the ICO opened, F2Pool constructed 31 transactions to the ICO smart contract from their addresses, without broadcasting the transactions to the network\footnote{Note that we don’t have an authoritative copy of the mempool over time, however, the probability of these transactions being broadcasted to the network and exclusively get mined by the same pool as the sender is really low.}. They used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.

>>>>

The second category of DApp in Table~\ref{tab:top25DApps} is crypto-collectables. Consider Cryptokitties~\cite{cryptokitties}, the most active DApp in this category and third most active overall. Each kitty (see Appendix~\ref{app:cryptokitty}) is a cartoon kitten with a set of unique features to distinguish it from other cryptokitties, some features are rarer and harder to obtain. They can be bought, sold, or bred with other cryptokitties. At the Ethereum level, the kitty is a token implemented with \textit{ERC-721: Non-Fungible Token Standard}~\cite{erc721}. Kitties are generally bought and sold on-chain through auction smart contracts. See Sections ~\ref{sec:frontrunningExchanges} and ~\ref{sec:ens} for more details on auction-based front-running attacks.

%ERC-721 are similar enough to ERC-20 tokens that they can be listed on exchanges that are ERC-20 compatible. To buy a kitty from their main website, the user sends the following bid transaction: \texttt{bid(uint256 \_tokenId)}. This is similar to open auctions and markets on section~\ref{sec:frontrunningExchanges}, bid value and the object (tokenId) bidding on is visible to the network and any user could easily front-run using insertion or displacement attack. The front-runner can see there is an interest in a specific kitty and insert a pair of transactions to buy it and re-auctioning it at a higher price, keeping any profit. %we call this auction-frontrunning.
% https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40

Specific to Cryptokitties protocol, they can breed and give birth. When cryptokitties breed, the smart contract sets from which future block the pregnancy of the cat can be completed. Anyone can complete the pregnancy by calling \texttt{giveBirth()} after the birthing block and they will receive a reward in ether\footnote{As there are no automated function calls in Ethereum, this incentive model --known as \textit{Action Callback}~\cite{klerosGeneralizedFrontrunner2019}-- is used to encourage users to call these functions.}. Even though front-running these calls would not affect the protocol workflow, but this displacement attack could result in financial profit for front-runners~\cite{zhou2018erays,cryptoMidwivesBot2018}.

@@

\textsf{Fomo3D} is an example of a game style (known as \textsf{Exit Scam}\footnote{\url{https://exitscam.me/play}}) not based on random outcomes, and it is the most active game on Ethereum in our sample. The aim of this game is to be the last person to have purchased a ticket when a timer goes to zero in a scenario where anyone can buy a ticket and each purchase increases the timer by 30 seconds. Many speculated such a game would never end but on August 22, 2018, the first round of the game ended with the winner collecting 10,469 Ether\footnote{The first winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}} equivalent to \$2.1M USD at the time.
Blockchain forensics indicate a sophisticated winning strategy to displace any new ticket purchases~\cite{fomo3dhacker,fomo3dmedium} that would reset the counter. The winner appears to have started by deploying many high gas consumption DApps unrelated to the game. When the timer of the game reached about 3 minutes, the winner bought 1 ticket and then sent multiple high gasPrice transactions to her own DApps. These transactions congested the network and bribed miners to prioritize them ahead of any new ticket purchases in \textsf{Fomo3D}. Recall this basic form of bribery is called a \textit{Gas Auction}; See related work ~\cite{mccorry2018smart,bonneau2016buy} for more sophisticated bribery contracts.

@@

The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at disintermediating central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS). For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and front-runners can displace other users attempting to register domains. This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}. \textsf{Ethereum Name Service (ENS)}~\cite{ensEIP} is the most active naming service on Ethereum. Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in a bid, but not the bid amount. Most implementations use the more user friendly but less confidential method for starting and bidding on a domain name: \texttt{startAuctionsAndBid()}. This method leaks the hash of the domain and the initial bid amount in the auction. Original names can be guessed from the hashes (\eg rainbow tables, used in ENS Twitter bot) or people can bid on domains even though they do not know what they are because of speculation on its value.

Users are allowed to bid for 3 days before the 48-hour reveal phase begins (see ~\ref{sec:comm}), in which all bidders (winners and losers) must send a transaction to reveal their bids for a specific domain or sacrifice their bid amount . Also note that if two bidders bid the same price, the first to reveal wins it.

Two strategies: (1) Attacker knows the domain name, then he makes sure he is first to reveal. (2) Attacker is speculating, so he waits to see other reveal, then insert myself with the information from the other reveal. (3) If my amount is bigger, I see other reveal and then reveal.

Displacement attack <--

A front-runner using the leaked information can bid with the same amount and reveal prior to the original bidder to win the auction~\cite{ENSHandlingFrontRunningDiscussion}. The auction model is similar to open auctions in \ref{sec:cryptogames}.

@@

\subsection{Data Collection and Analysis}
According to the analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started. When the ICO opened, F2Pool constructed 31 transactions to the ICO smart contract from their addresses, without broadcasting the transactions to the network\footnote{Note that we do not have an authoritative copy of the mempool over time, however, the probability of these transactions being broadcasted to the network and exclusively get mined by the same pool as the sender is low.}. They used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.
